A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-02-19 paper.tex
merge

Given a classical BRST theory $\cM$, we may consider the cotangent theory $T^*[-1]\cM$ whose action functional we denote by $S_g$.
\brian{
Why $S_g$? I suggest $S_0$, or $S_\cM$, or $S_{\rm cot}$. Also it's not clear from this sentence how $S_g$ depends on the data of the BRST theory. It doesn't use $S_{BRST}$, for instance.
} 
Let us denote the pullback of $S_{\mathrm{BRST}}$ along the obvious projection $T^*[-1]\cM\rightarrow \cM$ by the same letter. Then the equation $Q_{\mathrm{BRST}} S_{\mathrm{BRST}} = 0$ in $\oloc(\cM)$ implies that $\{S_g, S_{\mathrm{BRST}}\} = 0$ in $\oloc(T^*[-1]\cM)$.

@@

\vspace{-10pt}
\paragraph{Fields:} The BRST fields are given by:
\begin{itemize}
\item Gauge fields $A_{1, 0}\in\Omega^{1, 0}(M; \gg)$ and $A_{0, 1}\in\Omega^{0, 1}(M; \gg)$.
\item Scalar fields $a\in\Omega^{4,0}(M; \gg)[2]$ and $\wt a\in\Omega^{0, 4}(M; \gg)[-2]$.
\item Fermions $\chi\in\Omega^0(M; \gg)[-1]$, $B\in\Omega^{0, 2}(M; \gg)[-1]$, $\wt \chi\in\Omega^{0, 4}(M; \gg)[-1]$, $\rho\in\Omega^{1, 0}(M; \gg)[1]$ and $C\in\Omega^{3,0}(M; \gg)[1]$.
%Fermions $\chi\in\Omega^0(M; \gg)[-1]$, $B\in\Omega^{0, 2}(M; \gg)[-1]$, $\wt \chi\in\Omega^{0, 4}(M; \gg)[-1]$, $\rho\in\Omega^{1, 0}(M; \gg)[1]$ and $C\in\Omega^{3, 0}(M; \gg)[1]$.
\item A ghost field $c\in \Omega^0(M; \gg)[1]$.
\end{itemize}

@@

The claim about the underlying $\ZZ/2\ZZ$-graded theories follows by applying dimensional reduction (Proposition \ref{CS_to_BF_diml_red_prop}) to the computation of the minimal twist of 9d $\cN=1$ super Yang--Mills (Theorem \ref{thm:9dminimaltwist}). We are left to check that the equivalence respects  the gradings and the $\U(4)$-action. Indeed, the equivalence given by Theorem \ref{thm:9dminimaltwist} eliminates fields $A_{1, 0}, \wt a, \rho, \chi, \wt\chi$ and hence the underlying local $L_\infty$ algebra after the twist becomes
%\[
%\xymatrix@R=0.5cm@C=0.5cm{
%&\Omega^0(\CC^4; \gg)_c \ar[r] &\Omega^{0,1}(\CC^4; \gg)_{A_{0,1}} \ar[r] &\Omega^{0,2}(\CC^4; \gg)_{B} \ar[r] &\Omega^{0,3}(\CC^4; \gg)_{C^*} \ar[r] &\Omega^{0,4}(\CC^4; \gg)_{a^*} \\
%&&\ar@{}^{\bigoplus}[r] &&& \\
%\Omega^{4,0}(\CC^4; \gg)_{a} \ar[r] &\Omega^{4,1}(\CC^4; \gg)_C \ar[r] &\Omega^{4,2}(\CC^4; \gg)_{B^*} \ar[r] &\Omega^{4,3}(\CC^4; \gg)_{A_{0,1}^*} \ar[r] &\Omega^{4,4}(\CC^4; \gg)_{c^*}&
%}
%\]
\[
\xymatrix@R=0.5cm@C=0.5cm{
&\Omega^0(\CC^4; \gg)_c \ar[r] &\Omega^{0,1}(\CC^4; \gg)_{A_{0,1}} \ar[r] &\Omega^{0,2}(\CC^4; \gg)_{B} \ar[r] &\Omega^{0,3}(\CC^4; \gg)_{C^*} \ar[r] &\Omega^{0,4}(\CC^4; \gg)_{a^*} \\
&&\ar@{}^{\bigoplus}[r] &&& \\
\Omega^{4,0}(\CC^4; \gg)_{a} \ar[r] &\Omega^{4,1}(\CC^4; \gg)_C \ar[r] &\Omega^{4,2}(\CC^4; \gg)_{B^*} \ar[r] &\Omega^{4,3}(\CC^4; \gg)_{A_{0,1}^*} \ar[r] &\Omega^{4,4}(\CC^4; \gg)_{c^*}&
}
\]

concentrated in cohomological degrees $-1, \dots, 4$. These fields have the same degrees as in the holomorphic BF theory.
\end{proof}

@@

We will use the notation for fields of 8d $\cN=1$ super Yang--Mills from Section \ref{sect:8dholomorphictwist}. Using the Calabi--Yau structure we will regard $C\in\Omega^{0, 1}(\CC^4;\fg)[1]$, $\wt\chi\in\Omega^0(\CC^4;\fg)[-1]$, and $a \in \Omega^0(\CC^4 ; \fg)$. First, we are going to write the functionals \eqref{eq:gaugeI1} and \eqref{eq:gaugeI2} in terms of these fields.

\begin{prop}
The functionals $I^{(1)}$ and $I^{(2)}$ (see \eqref{eq:gaugeI1} and \eqref{eq:gaugeI2}) in terms of the fields of 8d $\cN=1$ super Yang--Mills are
\begin{align*}
S^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(C, A_{0, 1}^*) - (\wt \chi + t\chi)\wt a^*\right) \\
&+ \int\dvol\left((F_{0, 2}, B^*)  + (\ol\dd_{A_{0, 1}} a, C^*) + (t\dd_{A_{1, 0}} a, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*) + \frac{1}{2}[a, \wt a](\chi^*+t\wt\chi^*)\right) + t\Omega^{-1} F_{2, 0}\wedge B^* \\
S^{(2)}(Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + tac^*\right) + \frac{t}{2}\Omega^{-1}B^*\wedge B^* .
\end{align*}
\end{prop}

@@

\begin{align*}
S_{\mr{gauge}} &= \int\dvol\left(-(F_{2, 0}, F_{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2\right) + \frac 12 \left((\lambda_{1,0} \wedge \dd_{A_{1,0}} A_{0,2}) + \omega (\lambda_{1,0} \wedge \dbar_{A_{0,1}} \lambda_0) \right)  \\
S_{\mr{matter}} &= \int \dvol \bigg((\dd_{A_{1,0}}\phi , \ol \dd_{A_{0,1}} \gamma_0) + (\dd_{A_{1,0}}\gamma_0, \ol \dd_{A_{0,1}} \phi) + ([A_{0,2}, \beta_{2,0}], \phi) \bigg) + \beta_{2,0} \dbar_{A_{0,1}} \gamma_{0,1}  + \\
&\qquad + 2 (\omega \wedge ([\lambda_{1,0}, \gamma_{0,1}] ,\gamma_{0})  ) + \omega (\psi_0 \partial_{A_{1,0}} \gamma_{0,1}) \\
S_{\mr{anti}} &= \int \dvol \bigg((\dd_{A_{1, 0}} A_0, A_{1,0}^*) + (\ol\dd_{A_{0, 1}} A_0, A_{0,1}^*) \bigg) +  \\
& \qquad + \dvol \bigg([A_0, \lambda_0] \lambda_0^* + [A_0, A_{0,2}] A_{0,2}^* \bigg) + [\lambda_{1,0}, A_0] \wedge \lambda_{1,0}^* + \dvol \frac{1}{2}[A_0, A_0]A_0^*\\ 
&\qquad  + \dvol \bigg( [\phi, A_0] \phi^* + [\gamma_0, A_0] \gamma_0^*  + [\psi_0, A_0] \psi_0^* + [\beta_{2,0}, A_0] \beta_{2,0}^* \bigg) + [\gamma_{0,1}, A_0]\wedge \gamma_{0,1}^*\\
S^{(1)}_{\mr{gauge}} &=  \int  \dvol - (\lambda_{1,0} A_{1,0}^*)  + \frac 12  \left(F_{0,2}\wedge A_{0,2}^*+ \omega\wedge F_{1,1} \lambda_0^*  \right) \\
S^{(1)}_{\mr{matter}} &=  \int  \dvol \left( \psi_0 \phi^* + \frac 12 ( \ol \dd_{A_{0,1}} \gamma_{0} , \gamma_{0,1}^*) \right)\\
S^{(2)}_{\mr{gauge}} &= -\frac{1}{4}\int \dvol(\lambda_0^*)^2.
\end{align*}

>>>>

Given a classical BRST theory, we may consider the cotangent theory $T^*[-1]\cM$ whose action functional we denote by $S_g$. Let us denote the pullback of $S_{\mathrm{BRST}}$ along the obvious projection $T^*[-1]\cM\rightarrow \cM$ by the same letter. Then the equation $Q_{\mathrm{BRST}} S_{\mathrm{BRST}} = 0$ in $\oloc(\cM)$ implies that $\{S_g, S_{\mathrm{BRST}}\} = 0$ in $\oloc(T^*[-1]\cM)$.

@@

\vspace{-10pt}
\paragraph{Fields:} The BRST fields are given by:
\begin{itemize}
\item Gauge fields $A_{1, 0}\in\Omega^{1, 0}(M; \gg)$ and $A_{0, 1}\in\Omega^{0, 1}(M; \gg)$.
\item Scalar fields $a\in\Omega^{4,0}(M; \gg)[2]$ and $\wt a\in\Omega^{0, 4}(M; \gg)[-2]$.
\item Fermions $\chi\in\Omega^0(M; \gg)[-1]$, $B\in\Omega^{0, 2}(M; \gg)[-1]$, $\wt \chi\in\Omega^{0, 4}(M; \gg)[-1]$, $\rho\in\Omega^{1, 0}(M; \gg)[1]$ and $C\in\Omega^{4, 1}(M; \gg)[1]$.
%Fermions $\chi\in\Omega^0(M; \gg)[-1]$, $B\in\Omega^{0, 2}(M; \gg)[-1]$, $\wt \chi\in\Omega^{0, 4}(M; \gg)[-1]$, $\rho\in\Omega^{1, 0}(M; \gg)[1]$ and $C\in\Omega^{3, 0}(M; \gg)[1]$.
\item A ghost field $c\in \Omega^0(M; \gg)[1]$.
\end{itemize}
\brian{I've changed where $C$ lives to fit the proof below.}

@@

The claim about the underlying $\ZZ/2\ZZ$-graded theories follows by applying dimensional reduction (Proposition \ref{CS_to_BF_diml_red_prop}) to the computation of the minimal twist of 9d $\cN=1$ super Yang--Mills (Theorem \ref{thm:9dminimaltwist}). We are left to check that the equivalence respects  the gradings and the $\U(4)$-action. Indeed, the equivalence given by Theorem \ref{thm:9dminimaltwist} eliminates fields $A_{1, 0}, \wt a, \rho, \chi, \wt\chi$ and hence the underlying local $L_\infty$ algebra after the twist becomes
%\[
%\xymatrix@R=0.5cm@C=0.5cm{
%&\Omega^0(\CC^4; \gg)_c \ar[r] &\Omega^{0,1}(\CC^4; \gg)_{A_{0,1}} \ar[r] &\Omega^{0,2}(\CC^4; \gg)_{B} \ar[r] &\Omega^{0,3}(\CC^4; \gg)_{C^*} \ar[r] &\Omega^{0,4}(\CC^4; \gg)_{a^*} \\
%&&\ar@{}^{\bigoplus}[r] &&& \\
%\Omega^{4,0}(\CC^4; \gg)_{a} \ar[r] &\Omega^{4,1}(\CC^4; \gg)_C \ar[r] &\Omega^{4,2}(\CC^4; \gg)_{B^*} \ar[r] &\Omega^{4,3}(\CC^4; \gg)_{A_{0,1}^*} \ar[r] &\Omega^{4,4}(\CC^4; \gg)_{c^*}&
%}
%\]
\[
\xymatrix@R=0.5cm@C=0.5cm{
&\Omega^0(\CC^4; \gg)_c \ar[r] &\Omega^{0,1}(\CC^4; \gg)_{A_{0,1}} \ar[r] &\Omega^{0,2}(\CC^4; \gg)_{B} \ar[r] &\Omega^{0,3}(\CC^4; \gg)_{C^*} \ar[r] &\Omega^{0,4}(\CC^4; \gg)_{a^*} \\
&&\ar@{}^{\bigoplus}[r] &&& \\
\Omega^{4,0}(\CC^4; \gg)_{a} \ar[r] &\Omega^{4,1}(\CC^4; \gg)_C \ar[r] &\Omega^{4,2}(\CC^4; \gg)_{B^*} \ar[r] &\Omega^{4,3}(\CC^4; \gg)_{A_{0,1}^*} \ar[r] &\Omega^{4,4}(\CC^4; \gg)_{c^*}&
}
\]
concentrated in cohomological degrees $-1, \dots, 4$. These fields have the same degrees as in the holomorphic BF theory.
\end{proof}

@@

We will use the notation for fields of 8d $\cN=1$ super Yang--Mills from Section \ref{sect:8dholomorphictwist}. Using the Calabi--Yau structure we will regard $C\in\Omega^{0, 1}(\CC^4;\fg)[1]$ and $\wt\chi\in\Omega^0(\CC^4;\fg)[-1]$. First, we are going to write the functionals \eqref{eq:gaugeI1} and \eqref{eq:gaugeI2} in terms of these fields.

\begin{prop}
The functionals $I^{(1)}$ and $I^{(2)}$ (see \eqref{eq:gaugeI1} and \eqref{eq:gaugeI2}) in terms of the fields of 8d $\cN=1$ super Yang--Mills are
\begin{align*}
S^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(C, A_{0, 1}^*) - (\wt \chi + t\chi)\wt a^*\right) \\
&+ \int\dvol\left((F_{0, 2}, B^*)  + (\ol\dd_{A_{0, 1}} a, C^*) + (t\dd_{A_{1, 0}} \Tilde{a}, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*) + \frac{1}{2}[a, \wt a](\chi^*+t\wt\chi^*)\right) + t\Omega^{-1} F_{2, 0}\wedge B^* \\
S^{(2)}(Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + tac^*\right) + \frac{t}{2}\Omega^{-1}B^*\wedge B^* .
\end{align*}
\end{prop}

@@

\begin{align*}
S_{\mr{gauge}} &= \int\dvol\left(-(F_{2, 0}, F_{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2\right) + \frac 12 \left((\lambda_{1,0} \wedge \dd_{A_{1,0}} A_{0,2}) + \omega (\lambda_{1,0} \wedge \dbar_{A_{0,1}} \lambda_0) \right)  \\
S_{\mr{matter}} &= \int \dvol \bigg((\dd_{A_{1,0}}\phi , \ol \dd_{A_{0,1}} \gamma_0) + (\dd_{A_{1,0}}\gamma_0, \ol \dd_{A_{0,1}} \phi) + ([A_{0,2}, \beta_{2,0}], \phi) \bigg) + \beta_{2,0} \dbar_{A_{0,1}} \gamma_{0,1}  + \\
&\qquad + 2 (\omega \wedge ([\lambda_{1,0}, \gamma_{0,1}] ,\gamma_{0})  ) + \omega (\psi_0 \partial_{A_{1,0}} \gamma_{0,1}) \\
S_{\mr{anti}} &= \int \dvol \bigg((\dd_{A_{1, 0}} A_0, A_{1,0}^*) + (\ol\dd_{A_{0, 1}} A_0, A_{0,1}^*) \bigg) +  \\
& \qquad + \dvol \bigg([A_0, \lambda_0] \lambda_0^* + [A_0, A_{0,2}] A_{0,2}^* \bigg) + [\lambda_{1,0}, A_0] \wedge \lambda_{1,0}^* + \dvol \frac{1}{2}[A_0, A_0]A_0^*\\ 
&\qquad  + \dvol \bigg( [\phi, A_0] \phi^* + [\gamma_0, A_0] \gamma_0^*  + [\psi_0, A_0] \psi_0^* + [\beta_{2,0}, A_0] \beta_{2,0}^* \bigg) + [\gamma_{0,1}, A_0]\wedge \gamma_{0,1}^*\\
I^{(1)}_{\mr{gauge}} &=  \int  \dvol - (\lambda_{1,0} A_{1,0}^*)  + \frac 12  \left(F_{0,2}\wedge A_{0,2}^*+ \omega\wedge F_{1,1} \lambda_0^*  \right) \\
I^{(1)}_{\mr{matter}} &=  \int  \dvol \left( \psi_0 \phi^* + \frac 12 ( \ol \dd_{A_{0,1}} \gamma_{0} , \gamma_{0,1}^*) \right)\\
I^{(2)}_{\mr{gauge}} &= -\frac{1}{4}\int \dvol(\lambda_0^*)^2.
\end{align*}
